Post MCMCglmm analyses

### 2021-04-09 Analysis/06-post_mcmcglmm_analyses.Rmd
typo

```{r, fig.height = 4, fig.width = 8}
par(mfrow = c(1,2))
plot.all.axes(uncentered_major_axes,
         col = c("grey",colour_vector),
         add = FALSE, main = "Major axes (un-centred)")
plot.all.axes(uncentered_major_axes,
         col = c("grey",colour_vector),
         add = FALSE, main = "Major axes (level-centred)")
```

>>>>

```{r, fig.height = 4, fig.width = 8}
par(mfrow = c(1,2))
plot.all.axes(uncentered_major_axes,
         col = c("grey",colour_vector),
         add = FALSE, main = "Major axes (un-centred)")
plot.all.axes(level_centred_major_axes,
         col = c("grey",colour_vector),
         add = FALSE, main = "Major axes (level-centred)")
```
